Supporting information: Tail associations in ecological variables and their impact on extinction risk

### 2020-03-23 SuppMat.Rmd
starting to change appendices in trivial ways to accommodate journal style
made changes in Rmds as DAN said

```{r fig_agestr_mtd_linear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("moderate LT","moderate RT", expression(paste(Omega,"= ", infinity))), lty=c(1,1, NA),  
       col=c('red', 'blue', NA), horiz=F, bty='n', cex=1.5, x.intersp = 0.2
       #, seg.len = 1
       )
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf
xR<-las_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("extreme LT","extreme RT", expression(paste(Omega,"= ", infinity))), lty=c(1,1, NA),  
       col=c('red', 'blue', NA), horiz=F, bty='n', cex=1.5, x.intersp = 0.2
       #, seg.len = 1
       )
par(op)
dev.off()
```

@@

dt4_2<-tibble("$r_{min}$" = c("0",
                        "1",
                        "1",
                        "1.90",
                        "0",
                        "0"
))

@@

dt6<-tibble("$r_{bf}$" = c(r_bf_ricker,
                           r_bf_hassell,
                           r_bf_msmith,
                           r_bf_pennycuick,
                           r_bf_verhulst,
                           r_bf_abrewer
))

@@

<!--FIG: Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Ricker]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Ricker model.\label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Hassell]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Hassell model. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Maynard Smith]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Maynard Smith model. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Pennycuick]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Pennycuick model. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Verhulst]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Verhulst model. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--FIG: Austin-Brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Austin-Brewer]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Austin-Brewer model. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

@@

**The Ricker model.** The Ricker model was originally introduced in the context of modelling
the stock and recruitment of salmon populations, and has frequently been used in fisheries 
management. The model is 
$P(t+1)=F(P(t),r,K)=P(t) \exp[r(1-P(t)/K)]$, where $r>0$ is the intrinsic 
growth rate and $K>0$ is the carrying capacity of the population. There are two equilibrium 
states, $P_e = 0$ and $P_e = K$.
The equilibrium $P_e = 0$ is unstable, since ${F}' = \exp(r)$ for that equilibtrium, and 
$\exp(r) > 1$ for a positive $r$. Depending on $r$, 
the other equilibrium, $P_e = K$, can be stable or unstable, since ${F}' = (1-r)$. 
Specifically, $P_e=K$ is stable if $|1-r|<1$, i.e., $0<r<2$. 
The model shows undercompesatory dynamics if $0<r<1$ and overcompensatory dynamics
if $1<r<2$. Thus $r_{min}=0$, $r_c=1$, and $r_{bf}=2$.

**The Hassell model.** The Hassell model [@hassell1975density; @may1976bifurcations] was 
developed to help understand the dynamics of insect populations, and as a model of contest versus scramble 
intraspecific competition. The model
can be written $P(t+1) = F(P(t),r,a,b)=rP(t)/(1+aP(t))^b$. Here $r>0$ is the intrinsic growth rate and
$a$ and $b$ are positive parameters. If $b=1$, the Hassell model reduces to the
Beverton-Holt model [@beverton2012dynamics] used in fisheries. The Hassell model is a representation
of contest competition if $b \sim 1$, and scramble competition if $b$ is large.
Like the Ricker model, the Hassell model also has two equilibria, $P_e =0$ 
(the trivial extinction equilibrium) and $P_e = P^\star =(r^{1/b}-1)/a$. 
For $P_e = P^\star$, the model shows undercompensatory dymamics if $1<r<[b/(b-1)]^b$ 
and overcompensatory dynamics if $[b/(b-1)]^b<r<[b/(b-2)]^b$, so $r_{min}=1$, 
$r_c = [b/(b-1)]^b$, and $r_{bf}=[b/(b-2)]^b$.

**The Maynard Smith model.** The Maynard Smith 
model [@cohen1995unexpected; @maynard1978models; @may1976bifurcations] is
$P(t+1)=F(P(t),r,a,b)=rP(t)/[1+(aP(t))^b]$. Here $r>0$ is the growth rate and $a, b$ are 
positive parameters. The equilibria are $P_e=0$ (the extinction equilibrium) 
and $P_e = P^\star=\frac{1}{a}(r-1)^{1/b}$.
For a positive equilibrium value of $P^\star$, $r$ must be greater than $1$, so $r_{min}=1$. 
Then $P^\star$ will 
be a stable equilibrium and the model will show undercompensatory dynamics if $1<r<r_c=b/(b-1)$;
the model will show overcompensatory dymamics $r_c<r<b/(b-2)$.
$P^\star$ will become unstable for $r>r_{bf}=b/(b-2)$.

**The Pennycuick model.** The Pennycuick model [@pennycuick1968computer; @may1976bifurcations] 
is $P(t+1)=F(P(t),r,a,b)=rP(t)/[1+\exp \left\{-a(1-P(t)/b)\right\}]$, where 
$r>0$ is the intrinsic growth rate and $a$ and $b$ are positive parameters. Model
equilibria are 
$P_e=0$ (the extinction equilibrium) and $P_e=P^\star=\frac{b}{a}[a+\ln{(r-1)}]$. For 
a positive equilibrium population 
$r$ must be greater than $r_{min} = 1+\exp(-a)$. The transition point $r_c$ (from under- to 
overcompensatory dynamics) and the bifurcation point $r_{bf}$ were obtained
by numerical solution of ${F}'=0$ and ${F}'=-1$ at $P_e=P^{\star}$, respectively.

**The Verhulst model.** The Verhulst model 
[@cohen1995unexpected; @may1976bifurcations] is a discrete-time 
representation of logistic growth, and can be written 
as $P(t+1) = F(P(t),r,K) =P(t)[1+r(1-P(t)/K)]$, with $r>0$ and $K>0$ being growth rate and 
carrying capacity parameters, respectively. 
The model equilibrium $P_e=0$ is always unstable whereas the equilibrium 
$P_e=K$ is stable below the bifurcation 
point $r_{bf}=2$. The model shows undercompensatory dynamics for $0<r<r_c=1$
and overcompensatory dynamics for $r_c<r<r_{bf}$.

**The Austin-Brewer model.** The Austin-Brewer model 
[@austin1971world; @cohen1995unexpected] was originally used 
to model the growth of human populations. The model is $P(t+1) = F(P(t),r,K,s)= P(t)[1+r(K-P(t)) \left\{ 1-\exp (-sP(t))\right\}]$, where
$r, K, s$ are positive parameters. $r$ and $K$ represent the growth rate and carrying 
capacity, respectively.
the usual extinction equilibrium is $P_e=0$. The 
positive equilibrium is $P_e=P^\star=1-rK\left\{ 1-\exp (-sK)\right\}$. $P^\star$
is stable when $r<r_{bf}$ and unstable beyond the bifurcation point, where 
$r_{bf} = \frac{2}{K[1-\exp (-sK)]}$. The model shows undercompensatory dynamics when
$0<r<r_c$, where $r_c = \frac{1}{K[1-\exp (-sK)]}$. It shows 
overcompensatory dynamics when $r_c<r<r_{bf}$.

>>>>

```{r fig_agestr_mtd_linear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("moderate LT","moderate RT", 
                      #expression(paste(Omega,"%->%", infinity))
                      expression(symbol('\127') *symbol('\256')* symbol('\245'))
                      ), 
       lty=c(1,1, NA),  
       col=c('red', 'blue', NA), horiz=F, bty='n', cex=1.5, x.intersp = 0.2
       #, seg.len = 1
       )
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf
xR<-las_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("extreme LT","extreme RT", expression(symbol('\127') *symbol('\256')* symbol('\245'))), 
       lty=c(1,1, NA),  
       col=c('red', 'blue', NA), horiz=F, bty='n', cex=1.5, x.intersp = 0.2
       #, seg.len = 1
       ) 
par(op)
dev.off()
```

@@

dt4_2<-tibble("$r_\\text{min}$" = c("0",
                        "1",
                        "1",
                        "1.90",
                        "0",
                        "0"
))

@@

dt6<-tibble("$r_\\text{bf}$" = c(r_bf_ricker,
                           r_bf_hassell,
                           r_bf_msmith,
                           r_bf_pennycuick,
                           r_bf_verhulst,
                           r_bf_abrewer
))

@@

<!--FIG: Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Ricker]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Ricker model. Local dispersal.\label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Hassell]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Hassell model. Local dispersal.\label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Maynard Smith]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Maynard Smith model. Local dispersal.\label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Pennycuick]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Pennycuick model. Local dispersal.\label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Verhulst]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Verhulst model. Local dispersal.\label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--FIG: Austin-Brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Austin-Brewer]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Austin-Brewer model. Local dispersal.\label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

@@

**The Ricker model.** The Ricker model was originally introduced in the context of modelling
the stock and recruitment of salmon populations, and has frequently been used in fisheries 
management. The model is 
$P(t+1)=F(P(t),r,K)=P(t) \exp[r(1-P(t)/K)]$, where $r>0$ is the intrinsic 
growth rate and $K>0$ is the carrying capacity of the population. There are two equilibrium 
states, $P_e = 0$ and $P_e = K$.
The equilibrium $P_e = 0$ is unstable, since ${F}' = \exp(r)$ for that equilibtrium, and 
$\exp(r) > 1$ for a positive $r$. Depending on $r$, 
the other equilibrium, $P_e = K$, can be stable or unstable, since ${F}' = (1-r)$. 
Specifically, $P_e=K$ is stable if $|1-r|<1$, i.e., $0<r<2$. 
The model shows undercompesatory dynamics if $0<r<1$ and overcompensatory dynamics
if $1<r<2$. Thus $r_\text{min}=0$, $r_c=1$, and $r_\text{bf}=2$.

**The Hassell model.** The Hassell model [@hassell1975density; @may1976bifurcations] was 
developed to help understand the dynamics of insect populations, and as a model of contest versus scramble 
intraspecific competition. The model
can be written $P(t+1) = F(P(t),r,a,b)=rP(t)/(1+aP(t))^b$. Here $r>0$ is the intrinsic growth rate and
$a$ and $b$ are positive parameters. If $b=1$, the Hassell model reduces to the
Beverton-Holt model [@beverton2012dynamics] used in fisheries. The Hassell model is a representation
of contest competition if $b \sim 1$, and scramble competition if $b$ is large.
Like the Ricker model, the Hassell model also has two equilibria, $P_e =0$ 
(the trivial extinction equilibrium) and $P_e = P^\star =(r^{1/b}-1)/a$. 
For $P_e = P^\star$, the model shows undercompensatory dymamics if $1<r<[b/(b-1)]^b$ 
and overcompensatory dynamics if $[b/(b-1)]^b<r<[b/(b-2)]^b$, so $r_\text{min}=1$, 
$r_c = [b/(b-1)]^b$, and $r_\text{bf}=[b/(b-2)]^b$.

**The Maynard Smith model.** The Maynard Smith 
model [@cohen1995unexpected; @maynard1978models; @may1976bifurcations] is
$P(t+1)=F(P(t),r,a,b)=rP(t)/[1+(aP(t))^b]$. Here $r>0$ is the growth rate and $a, b$ are 
positive parameters. The equilibria are $P_e=0$ (the extinction equilibrium) 
and $P_e = P^\star=\frac{1}{a}(r-1)^{1/b}$.
For a positive equilibrium value of $P^\star$, $r$ must be greater than $1$, so $r_\text{min}=1$. 
Then $P^\star$ will 
be a stable equilibrium and the model will show undercompensatory dynamics if $1<r<r_c=b/(b-1)$;
the model will show overcompensatory dymamics $r_c<r<b/(b-2)$.
$P^\star$ will become unstable for $r>r_\text{bf}=b/(b-2)$.

**The Pennycuick model.** The Pennycuick model [@pennycuick1968computer; @may1976bifurcations] 
is $P(t+1)=F(P(t),r,a,b)=rP(t)/[1+\exp \left\{-a(1-P(t)/b)\right\}]$, where 
$r>0$ is the intrinsic growth rate and $a$ and $b$ are positive parameters. Model
equilibria are 
$P_e=0$ (the extinction equilibrium) and $P_e=P^\star=\frac{b}{a}[a+\ln{(r-1)}]$. For 
a positive equilibrium population 
$r$ must be greater than $r_\text{min} = 1+\exp(-a)$. The transition point $r_c$ (from under- to 
overcompensatory dynamics) and the bifurcation point $r_\text{bf}$ were obtained
by numerical solution of ${F}'=0$ and ${F}'=-1$ at $P_e=P^{\star}$, respectively.

**The Verhulst model.** The Verhulst model 
[@cohen1995unexpected; @may1976bifurcations] is a discrete-time 
representation of logistic growth, and can be written 
as $P(t+1) = F(P(t),r,K) =P(t)[1+r(1-P(t)/K)]$, with $r>0$ and $K>0$ being growth rate and 
carrying capacity parameters, respectively. 
The model equilibrium $P_e=0$ is always unstable whereas the equilibrium 
$P_e=K$ is stable below the bifurcation 
point $r_\text{bf}=2$. The model shows undercompensatory dynamics for $0<r<r_c=1$
and overcompensatory dynamics for $r_c<r<r_\text{bf}$.

**The Austin-Brewer model.** The Austin-Brewer model 
[@austin1971world; @cohen1995unexpected] was originally used 
to model the growth of human populations. The model is $P(t+1) = F(P(t),r,K,s)= P(t)[1+r(K-P(t)) \left\{ 1-\exp (-sP(t))\right\}]$, where
$r, K, s$ are positive parameters. $r$ and $K$ represent the growth rate and carrying 
capacity, respectively.
the usual extinction equilibrium is $P_e=0$. The 
positive equilibrium is $P_e=P^\star=1-rK\left\{ 1-\exp (-sK)\right\}$. $P^\star$
is stable when $r<r_\text{bf}$ and unstable beyond the bifurcation point, where 
$r_\text{bf} = \frac{2}{K[1-\exp (-sK)]}$. The model shows undercompensatory dynamics when
$0<r<r_c$, where $r_c = \frac{1}{K[1-\exp (-sK)]}$. It shows 
overcompensatory dynamics when $r_c<r<r_\text{bf}$.
